---
title: "Untitled"
author: "Jonathan Bourne"
date: "13 July 2017"
output: html_document
---


```{r}

packages<- c("tidyverse", "rvest", "tm.plugin.lexisnexis", "tidytext", "stringr", "tm", "ggfortify", "Rtsne", "xtable", "htmlTable")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


lapply(packages, library, character.only = TRUE)
#used for doing operation in the corpus
PatternReplace <- content_transformer(function(x, pattern, replacement) gsub(pattern, replacement, x))

setwd("/home/jonno/FestivalAnalysis/FestivalAnalysis/Functions")
list.files() %>% sapply(.,source)



```

cost
http://www.money.co.uk/guides/how-much-do-festivals-cost-and-what-should-you-take.htm

```{r}


FestivalData <-data_frame(Festival = c("Notting Hill", "Glastonbury", "FSTVL", "Lovebox", "Wireless", "SW4", "T in the park", "Reading.Festival", "Bestival", "Leeds", "London August 16"),
           Capacity = c(1e6, 1.35e5, 1.5e4, 5e4, 5e4, 2e4, 7e4, 9e4,8e4, 8e4, 8.8e6),
           Days = c(2,5,3,2,3,2, 4, 3, 4, 3, 31)) %>%
  mutate(PersonDays =  Capacity*Days) %>% 
  arrange(Capacity)


write_excel_csv(FestivalData, "FestivalData.xlsx")

FestivalData %>%
  htmlTable(.,
            caption ="Click on headings to rearrange according to size")

```

#London Crime
  nature of crime

http://www.britishbids.info/wp-content/uploads/Policing-the-Night-Time-Economy.pdf
#crime stats
  https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/bulletins/crimeinenglandandwales/yearendingdec2016

https://data.london.gov.uk/dataset/the-number-of-public-houses-and-bars-in-london-2001-2016/resource/7fa8d10c-e2bd-49e2-8db3-5ac2659c502b

liscened premises
https://www.gov.uk/government/statistics/entertainment-licensing-2014


This is challenging to do 

The nature of crime tables show that 47% of violent crime occurs at the weekend
62% of violent crime occurs in the evening
11% occur in pubs and clubs
80% of weekend arrests are alchohol related -The Institute of Alcohol Studies 
25% of all crime occurs at night
70% of weekend violent incidents involved alchohol



```{r}
setwd("/home/jonno/FestivalAnalysis")



LondonPop<-8.8e6
Alldays <- 30
ViolentCrime <- 16.6e3
WeekendDays <- 9


#make a reclassing table to formatt the classes like I have for the festivals
Reclassing <- "Anti-social behaviour,Burglary,Criminal damage and arson,Other theft,Public order,Vehicle crime,Violence and sexual offences,Drugs,Robbery,Shoplifting,Theft from the person,Other crime,Possession of weapons,Bicycle theft" %>% str_split(.,pattern=",") %>%
  unlist %>%
  data_frame(OldClass = .,
NewClass = c("Other", "Theft", "Other", "Theft", "Other", "Other", "Violent and Sexual", "Drugs", "Robbery", "Theft", "Theft", "Other", "Weapons", "Theft"))


LondonCrime7 <-read_csv("2016-07-metropolitan-street.csv")  %>%
  mutate(`Crime type`=Reclassing$NewClass[match(.$`Crime type`, Reclassing$OldClass)]) %>%
  group_by(`Crime type`) %>%
  summarise(counts = n()) %>% 
  mutate(Rate = (counts/(LondonPop*Alldays))*1e6)

#Crime was lower in August so let's use that instead of june

LondonCrime8 <-read_csv("2016-08-metropolitan-street.csv")  %>%
  mutate(`Crime type`=Reclassing$NewClass[match(.$`Crime type`, Reclassing$OldClass)]) %>%
  group_by(`Crime type`) %>%
  summarise(counts = n()) %>%
  mutate(Festival = "London August 16") %>%
  spread(key= `Crime type`, value = counts)

# %>% 
#   bind_rows(.,data_frame(`Crime type`= "Total", counts =sum(.$counts))) %>%
#   mutate(London = (counts/(LondonPop*Alldays))*1e6) %>%
#   mutate(NottingHill = (c(170,95,33,264,132,41,735)/(1e6*2))*1e6)


#slightly lower than August

LondonCrime9 <-read_csv("2016-09-metropolitan-street.csv")  %>%
  mutate(`Crime type`=Reclassing$NewClass[match(.$`Crime type`, Reclassing$OldClass)]) %>%
  group_by(`Crime type`) %>%
  summarise(counts = n()) %>% 
  mutate(Rate = (counts/(LondonPop*Alldays))*1e6)

NHCVS <- (132/(1e6*2))*1e6

LondonVSNHC <- c((ViolentCrime/(LondonPop*Alldays))*1e6,

(ViolentCrime*.47/(LondonPop*WeekendDays))*1e6,

(ViolentCrime*.47*0.7/(LondonPop*WeekendDays))*1e6,

NHCVS) %>% round %>% 
  data_frame(Type = c("London", "London at weekends", "London wknds alchohol", "Notting Hill"), `Crime Rate` = .) %>%
  mutate(`Percent Difference` = signif(`Crime Rate`/NHCVS,3)*100-100)



 CrimeBreakdown %>% mutate(`Violent and Sexual` = Sex + Violent)


```



#Sources

##Glasto
https://www.whatdotheyknow.com/request/crime_statistics_from_glastonbur
22-26 June
1449 articles


##Notting Hill
https://www.whatdotheyknow.com/request/notting_hill_carnival_crime

435 articles about 260 unique

##FSTVL lovebox wireless sw4
https://beta.met.police.uk/globalassets/foi-media/disclosure_2017/april_2017/information-rights-unit--quantities-of-crimes-recorded-against-under-each-category-of-victim-based-crime-other-crimes-against-society-and-fraud-offences
FSTVL 28-29 may
Wireless 8-10 jul
SW4 27-28 August


##T in the park
https://www.whatdotheyknow.com/request/388712/response/948315/attach/3/2011%202016%20Crime%20Stats.pdf
7-10 july

#Reading
This data source is not very good they added up the totals incorrectly, however the police claim in an foi they don't have data which is odd becuase the newspaper is quoting them
http://www.readingchronicle.co.uk/news/14720956.Reading_Festival_2016__Crime_rate_down_20_per_cent_on_last_year__new_figures_show/
26-28 August

##Bestival
NOt that gret a data source
http://www.iwcp.co.uk/news/news/police-praise-bestival-despite-rise-in-some-crimes-96145.aspx
8-11 September


```{r}

 CrimeBreakdown <-  data_frame('Notting Hill'= c(105,264,170,27,33,41,95), 
                             "Glastonbury" = c(16,154,32,2,0,1,0),
                             "FSTVL" = c(0,51,9,1,5,0,1),
                             "Lovebox" = c(9,33,19,2,0,0,0),
                             "Wireless" = c(14,38,9,3,3,0,0),
                             "SW4" = c(6,50,14,1,2,0,0),
                             "T in the park" = c(29,95,381,3,1,1,20),
                             "Reading.Festival" = c(0,104,30,2,6,0,0),
                             "Bestival" = c(13,146,30,1,0,0,12),
                             "Leeds" = c(12,129, 38,1,3,2,13),
                            Type = c("Violent", "Theft", "Drugs", "Sex", "Robbery", "Weapons", "Other")) %>%
  gather(key = Festival, Crimes,-Type) %>%
  spread(key = Type, value = Crimes) %>%
  mutate(`Violent and Sexual` = Sex + Violent) %>%
  select(-Sex, -Violent) %>%
  bind_rows(., LondonCrime8) %>%
  mutate(Total = rowSums(.[-1]),
         Exp = rowSums(.[-c(1,2,6)]))%>% 
  arrange(Festival) %>%
     setNames(make.names(names(.)))

write_excel_csv(CrimeBreakdown, "CrimeBreakdown.xlsx")

 CrimeBreakdownRate <- FestivalData %>% select(Festival, PersonDays) %>%
  left_join(CrimeBreakdown, by = "Festival") %>% 
  mutate_if(is.numeric, funs(FestivalData$PersonDays/.)) %>%
    mutate_if(is.numeric, funs(1/.)) %>%
   select(-PersonDays) 

 #rate per 1e6
test <- FestivalData %>% select(Festival, PersonDays) %>%
  left_join(CrimeBreakdown, by = "Festival") %>% 
  mutate_if(is.numeric, funs(FestivalData$PersonDays/.)) %>%
    mutate_if(is.numeric, funs(round((1/.)*1e6))) %>%
   select(-PersonDays) 

write_excel_csv(test, "CrimeBreakdownRate.xlsx")

CrimeBreakdownRate %>%  
  mutate_if(.,is.numeric, funs(round(.*1e6))) %>%
  arrange(Total) %>%
 htmlTable(.,
           caption = "This table show the number of crimes per million. Column on far right excludes Drugs and weapons possesion")

 CrimeBreakdownPP <-  CrimeBreakdownRate%>%
 mutate_if(.,is.numeric, funs((1/.))) 

 
 
RatePCA <- CrimeBreakdownRate[,c(3:5,7)] %>%
  prcomp()
# 
# RatePCA <- CrimeBreakdownRate%>%
#   mutate(seperator = ifelse(Festival == "Notting Hill", 1,0)) %>%
#   .[,c(2:6,11)] %>%
#   prcomp()
summary(RatePCA) #first two componants capture 99.7 percent of variance

autoplot(RatePCA, data = CrimeBreakdownRate, colour = "Festival", loadings = TRUE, loadings.label = TRUE) 
 

RatePCA <- prcomp(CrimeBreakdownRate[,3:5])
summary(RatePCA) #first two componants capture 99.7 percent of variance

autoplot(RatePCA, data = CrimeBreakdownRate, colour = "Festival", loadings = TRUE, loadings.label = TRUE) +
  ggtitle("")
```

#Ranking Festivals
```{r}

 CrimeBreakdownPP %>% mutate_if(is.numeric, funs(rank(-.))) %>%
  mutate(AverageRank = rowMeans(.[-1]),
         RankAvgRank = rank(AverageRank),
         AverageRank = round(AverageRank))

```




#getting lexis nexis

##Nottinghill

```{r}
setwd("/home/jonno/FestivalAnalysis")
GlastonburyDATA <- ProcessArticles("Glastonbury")
NottingHillDATA <- ProcessArticles("Notting Hill")
WirelessDATA <- ProcessArticles("Wireless")
BestivalDATA <- ProcessArticles("Bestival")
ReadingDATA <- ProcessArticles("Reading Festival")
LeedsDATA <- ProcessArticles("Leeds")
TparkDATA <- ProcessArticles("T in the park")
#RioDATA <- ProcessArticles("Rio") #RIo is dominated by ZIKA coverage which was high at the time.
```


```{r}
Comparefest <- ls(pattern=("DATA")) %>%
  map_df(~eval(parse(text =paste0(.x,"$FestivalSentiment")))) %>%
  spread(key = Festival, value = count) 

PercentFest <- Comparefest  %>% setNames(make.names(names(.))) %>%
  mutate(type = ifelse(sentiment=="positive"| sentiment == "negative", "direction", "emotions")) %>%
 group_by(type) %>%
  mutate_if(is.numeric, funs(./sum(.)))%>% 
  arrange(type)  %>% ungroup

PercentFest2 <- PercentFest %>% 
  select(-type) %>%
  gather(key = "Festival", value = "value",-sentiment) %>%
  spread(key=sentiment, value = value)

summary(prcomp(PercentFest2[,-c(1)]))

autoplot(prcomp(PercentFest2[,-c(1)]), data = PercentFest2, colour = "Festival", loadings = TRUE, loadings.label = TRUE) +
  ggtitle("2-D projection for the emotional content of media coverage of UK Festivals")
ggsave("MediaPreTreat.png")

PercentFest2 %>% 
  left_join(.,CrimeBreakdownPP %>% mutate(Festival = make.names(Festival))) %>%
  ggplot(., aes(y= fear, x = Total)) +geom_point()

RelativetoGlasto <- PercentFest%>%
  mutate_if(is.numeric, funs(./rowMeans(PercentFest[,-c(1,9)])))


RelativetoGlasto %>%
  mutate_if(is.numeric, funs(round(.*100)-100)) %>%
  select(-type) %>%
  htmlTable(.,
            caption = "This table shows the emotional coverage of each festival relative to average. Scores above 0 mean more than average")

```

Interpret the emotional content
```{r}

TopWordsForEmotions <- unique(NottingHillDATA$SentiWords$sentiment) %>% map(~TopEmotions(.x))
names(TopWordsForEmotions) <- unique(NottingHillDATA$SentiWords$sentiment)

allemotions <- "white black opera john boy khan lord wireless festival carnival parade vote leave resign resignation government resigned holiday reading" %>% str_split(pattern =  " ") %>% unlist

fear <- "watch mum destination advance volunteer journey confidence government change feeling parade youth giant bear god belt lace khan" %>% str_split(pattern = " ")%>% unlist

trust <- "smith police bank iron hospital officer" %>% str_split(pattern = " ")%>% unlist

disgust <- "glitter tree celebrity winning lush treat octopus" %>% str_split(pattern = " ")%>% unlist

anger <- "hot musical orchestra harry celebrity"  %>% str_split(pattern = " ")%>% unlist

positive <- "police officer director" %>% str_split(pattern = " ")%>% unlist
sadness <- "musical art mother music" %>% str_split(pattern = " ")%>% unlist
negative <- "pop mum mother parade" %>% str_split(pattern = " ")%>% unlist

sentstreat<- get_sentiments("nrc") %>% 
  mutate(joint = paste0(word, sentiment)) %>%
  filter(!(word) %in% allemotions) %>%
  filter(!(joint) %in% paste0(fear, "fear")) %>%
  filter(!(joint) %in% paste0(trust, "trust")) %>%
  filter(!(joint) %in% paste0(disgust, "disgust")) %>%
  filter(!(joint) %in% paste0(anger, "anger")) %>%
  filter(!(joint) %in% paste0(positive, "positive")) %>%
  filter(!(joint) %in% paste0(sadness, "sadness")) %>%
  filter(!(joint) %in% paste0(negative, "negative")) %>%
  select(-joint)

test <- get_sentiments("nrc") %>% 
     filter((word %in% c("festival", "carnival", "boy", "holiday",  "parade")) )


```

#Adapted sentiments

```{r}
setwd("/home/jonno/FestivalAnalysis")
GlastonburyTREAT <- ProcessArticles("Glastonbury", sentstreat)
NottingHillTREAT <- ProcessArticles("Notting Hill", sentstreat)
WirelessTREAT <- ProcessArticles("Wireless", sentstreat)
BestivalTREAT <- ProcessArticles("Bestival", sentstreat)
ReadingTREAT <- ProcessArticles("Reading Festival", sentstreat)
LeedsTREAT <- ProcessArticles("Leeds", sentstreat)
TparkTREAT <- ProcessArticles("T in the park", sentstreat)
```


#total words
```{r}
  
totalwords<-ls(pattern=("TREAT")) %>%
  map_dbl(~eval(parse(text =paste0(.x,"$TotalWords"))))

totalwords<-  FestivalData %>%
    filter(!grepl("London|FSTVL|SW4|Lovebox", Festival)) %>%
    arrange(Festival) %>%
  mutate(Words = totalwords,
         WordsperPersondays = round((Words/PersonDays)*1000),
         WordsperCapacity = round((Words/Capacity)*1000)) %>%
  select(Festival,Words, WordsperPersondays, WordsperCapacity)

totalwords %>%
  htmlTable()

 
```



#Post treatment analysis

```{r}
ComparefestTreat <- ls(pattern=("TREAT")) %>%
  map_df(~eval(parse(text =paste0(.x,"$FestivalSentiment")))) %>%
  spread(key = Festival, value = count) 

PercentFestTreat <- ComparefestTreat  %>% setNames(make.names(names(.))) %>%
  mutate(type = ifelse(sentiment=="positive"| sentiment == "negative", "direction", "emotions")) %>%
 group_by(type) %>%
  mutate_if(is.numeric, funs(./sum(.)))%>% 
  arrange(type)  %>% ungroup

PercentFestTreat2 <- PercentFestTreat %>% 
  select(-type) %>%
  gather(key = "Festival", value = "value",-sentiment) %>%
  spread(key=sentiment, value = value)

summary(prcomp(PercentFestTreat2[,-c(1)]))

autoplot(prcomp(PercentFestTreat2[,-c(1)]), data = PercentFestTreat2, colour = "Festival", loadings = TRUE, loadings.label = TRUE) +
  ggtitle("2-D projection for the emotional content of media coverage of UK Festivals\n after cleaning the sentiments")
ggsave("MediaPostTreat.png")

RelativetoGlastoTreat <- PercentFestTreat%>%
  mutate_if(is.numeric, funs(./rowMeans(PercentFestTreat[,-c(1,9)])))

RelativetoGlastoTreat %>%
  mutate_if(is.numeric, funs(round(.*100)-100)) %>%
  select(-type) %>%
  htmlTable(., 
            caption = "This table shows the emotional coverage of each festival relative to average. Scores above 0 mean more than average")


TopWordsForEmotionsTreat <- unique(NottingHillDATA$SentiWords$sentiment) %>% map(~TopEmotions(.x, top = 6, patt = "TREAT")) %>%
  setNames(unique(NottingHillDATA$SentiWords$sentiment))


NottingHillTREAT$TotalWords
test<- NottingHillTREAT$TopWords
test<- left_join(NottingHillTREAT$TopWords, sentstreat, by = c("term" = "word"))


topwords <- ls(pattern=("TREAT")) %>%
  map_df(~eval(parse(text =paste0(.x,"$TopWords"))) %>%
           slice(1:20) %>%
           mutate(Festival =sub("TREAT", "", .x),
         number = 1:20)) %>%
  select(-counts) %>%
  spread(key=Festival, value = "term")


WordsByFestival <- ls(pattern=("TREAT")) %>%
  map_df(~eval(parse(text =paste0(.x,"$TopWords"))) %>%
           mutate(Festival =sub("TREAT", "", .x),
                  rank = 1:n())) %>%
  select(-counts) %>%
  spread(key=Festival, value = "term")

wordstomatch <-c("police", "attack", "violence", "hospital")
WordsByFestival %>% map_df(~match(wordstomatch,.x )) %>%
  mutate(Word = wordstomatch) %>%
  select(Word, Bestival:Wireless) %>%
  htmlTable(.,
            caption="Word frequency per 1000")

#get word frequency of key negative words

totalwords2 <- totalwords
totalwords2[c(4:6),1] <- c("NottingHill", "Reading", "Tpark") 

WordsByFestiva2 <- ls(pattern=("TREAT")) %>%
  map_df(~eval(parse(text =paste0(.x,"$TopWords"))) %>%
           mutate(Festival =sub("TREAT", "", .x))) %>%
  left_join(.,totalwords2 %>% select(Festival, Words)) %>%
  mutate(Frequency = signif((counts/Words)*1000,2)) %>% 
  group_by(Festival) %>%
  mutate(EmoFreq = (counts/sum(counts))*1000) %>%
  filter(term %in% wordstomatch) %>%
  select(Festival, Frequency, term) %>%
  spread(key = Festival, value = Frequency) 

WordsByFestiva2[is.na(WordsByFestiva2)] <-0

WordsByFestiva2 %>%
  htmlTable(.,
            caption="Word frequency per 1000, click on headings to rearrange")




topwords2 <-topwords %>%
  slice(1:10) %>%
  rename(Rank = number) %>%select(-Rank)

#adds padding to stop the tables looping cramped
spacing<- rbind(rep("background: lightgrey; font-size: 1em; padding-left: .5em; padding-right: .2em;", times=ncol(topwords2)),
                           matrix("", ncol=ncol(topwords2), nrow=nrow(topwords2)))

topwords2 %>%
  htmlTable()


```



Horrible models
```{r}
errors <- PercentFestTreat2 %>% #ComparePaper2 %>%
  left_join(.,CrimeBreakdownPP %>% mutate(Festival = make.names(Festival))) 

errors %>%
  filter(fear != 1) %>%
#    filter(Festival != "T.in.the.park") %>%
ggplot(., aes(x= Total, fear)) +geom_point()

errors %>%
  lm(fear~Total, data = .) %>% summary

errors %>%
  filter(Festival != "Notting.Hill") %>%
  lm(fear~Total, data = .) %>% summary

errors %>%
  filter(Festival != "T.in.the.park") %>%
  lm(fear~Total, data = .) %>% summary


```
Models show that coverage has no relationship to crime unless you remove Notting Hill then fear reduces as crime reduces, or you remove T in the Park in which case fear increases as crime reduces.


#Coverage by newpapers


```{r}
ComparePaper <- ls(pattern=("TREAT")) %>%
  map_df(~eval(parse(text =paste0(.x,"$SentimentbyPaper"))) %>%
           gather(key = Paper, value = "value",-sentiment) %>%
           mutate(Festival = sub("TREAT", "", .x))) 

ComparePaper2<-    ComparePaper%>%
  mutate(type = ifelse(sentiment=="positive"| sentiment == "negative", "direction", "emotions")) %>%
      group_by(Paper, Festival, type) %>%
      mutate(value = value/sum(value)) %>%
  ungroup %>%
  select(-type) %>%
  spread(key = sentiment, value = value) %>%
  mutate(Nott = ifelse(Festival =="NottingHill","NottingHill", "Other"))

PaperPCA <- ComparePaper2 %>% .[,c(3:12)] %>%
  prcomp()

summary(PaperPCA) #first two componants capture 99.7 percent of variance

autoplot(PaperPCA, data = ComparePaper2, colour = "Nott", loadings = TRUE, loadings.label = TRUE) 
 
```


extract Journo names etc
```{r}


NottDat <- LexisNexisSource("Notting Hill UK_National_Newspapers2017-07-13_12-35.HTML", encoding = "UTF-8") 
NottDat2 <- NottDat %>%
  Corpus(., readerControl = list(language = NA))

test <- grep("BYLINE:", NottDat$content)

NottDat$content[test]

meta(NottDat2)
meta(NottDat2[[1]])

as.data.frame(meta(NottDat2[[1]]))

type<- (meta(NottDat2[[1]])) 
inspect(NottDat2[[1]])

test <- NottDat2 %>% map_df(~meta(.x))

NottDat2 %>% map_df(~meta(.x, tag = "author") )
test <- sapply(NottDat2, meta, "author")
```

